Cheat Sheet for PFPL

### 2016-11-11 pfpl/draftcheatsheet.tex
Added @ (map)
Bring draft up to Chapter 41

91& 365 & $ \$ E$ & Dollar  & Synchronize & Synchronize parallel processes \\
92& 365 & $E_1 + E_2 $ & Plus  & Choice & Pick one of 2 expressions \\
93& 365 & $?a;P$ & Query  & Query & Query a channel \\
94& 365 & $!a;P$ & Bang  & Signal & Signal a channel \\
95 & 367 & $ P_1 \otimes P_2 $  & Circle times & Composition & Compose 2 concurrent processes \\
96 & 369 & $ *P $  & Star & Replication & Replicate process $P$ \\
97 & 373 & $ ! a ( e ; P ) $  & Bang & Send & Send expression $e$ on channel $a$ to process $P$ \\
98 & 373 & $ ? a ( x . P ) $  & Query & Receive & Receive expression $e$ on channel $a$ in process $P$ \\

>>>>

91& 365 & $ \$ E$ & Dollar  & Synchronize & Synchronize parallel processes \\
92& 365 & $E_1 + E_2 $ & Plus  & Choice & Pick one of 2 expressions \\
93& 365 & $?a;P$ & Query  & Query & Query a channel \\
94& 365 & $!a;P$ & Bang  & Signal & Signal a channel \\
95 & 367 & $ P_1 \otimes P_2 $  & Circle times & Composition & Compose 2 concurrent processes \\
96 & 367 & $P \overset{\alpha}{\longmapsto} P' $ & Maps to & Steps & $P$ steps to $P'$ if action $\alpha$ is permissible \\
97 & 369 & $ *P $  & Star & Replication & Replicate process $P$ \\
98 & 370 & $ \nu a . P $ & Nu & New channel & Declare new channel $a$ in process $P$ \\
99 & 371 & $P \overset{\alpha}{\underset{\Sigma}{\longmapsto}} P' $ & Maps to & Steps & $P$ steps to $P'$ if action $\alpha$ is permissible in context $\Sigma$ \\
100 & 373 & $ ! a ( e ; P ) $  & Bang & Send & Send expression $e$ on channel $a$ to process $P$ \\
101 & 373 & $ ? a ( x . P ) $  & Query & Receive & Receive expression $e$ on channel $a$ in process $P$ \\
102 & 376 & $ \tau $ chan & Tau & Channel type & Channel of type $\tau$ \\
103 & 376 & $ \& a $ & Ampersand & Channel reference & Reference to channel $a$ \\
104 & 376 & $ !!(e_1;e_2;P) $ & Bang bang & Send & Send message on channel $e_1$  \\
105 & 376 & $ ??(e;x.P) $ & Query query & Receive & Receive message on channel $e$  \\
106 & 377 & $ @ $ & At & Map & Maps lambda expressions to PiC \\
\end{tabular}

\subsubsection*{40 Concurrent Algol}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

107& 382 & $ P_1 \otimes P_2 $ & Circle times  & Concurrent & Run processes $P_1$ and $P_2$ concurrently \\
108 & 382 & $ \nu a ~\tau . p $ & Nu & New channel & Create a new chanell \\
109 & 383 & $ m \overset{\alpha}{\underset{\Sigma}{\Rightarrow}} \nu \Sigma ' \{ m' \otimes p'\} $ & Fat right arrow & Transitions & Command $m$ transitions to command $m'$ while creating new channels $\Sigma$  and
new processes $p'$ . The action $\alpha$ specifies the interactions of which $m$ is capable when executed. \\
\end{tabular}

\subsubsection*{41 Distributed Algol}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

110 & 392 & $ a~\tau @ w $ & Tilde  & Declare & $a$ is a channel at site $w$ carrying payloads of type $\tau$ \\
\end{tabular}
